Interval Probability for Fuzzy Quantum Theories

### 2016-06-13 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities} Updates...

Similar to the classical case, to know the quantum probability for
each event, we can apply the law of large number, and measure the
relative frequency. For example, Stern and Gerlach found a silver
atoms beam deflected in a highly inhomogeneous magnetic field~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
Ideally, if the local field strength directs to the $z$-axis, and
all particles have the same velocity, three spots will be produced
corresponding to $\ket{0}$ and $\ket{1}$. In reality, the local
field strength cannot prefect directs to to the $z$-axis, and all
atoms come from a hot oven cannot have the same velocity. The variant
of velocity makes spots broader and more washed out so that it may
sometimes hard to decide a particle corresponding to which state\footnote{\yutsung{Citation here?}}.
Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$. About the imperfect direction of
field strength, we might take it into account when we introduce the
discrete quantum theory later.

>>>>

Similar to the classical case, to know the quantum probability for
each event, we can apply the law of large number, and measure the
relative frequency. For example, Stern and Gerlach found a silver
atoms beam deflected in a highly inhomogeneous magnetic field~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
Ideally, if the local field strength directs to the $z$-axis, and
all particles have the same velocity, three spots will be produced
corresponding to $\ket{0}$ and $\ket{1}$. In reality, we need a
lot of resource to keep the local field of strength directing to the
$z$-axis, to keep the atoms having similar velocity, and to point
out the position each particle landed on.

If the field of strength does not perfectly direct to the $z$-axis,
we does not really test the quantum event we want to test, and we
will go back to this problem when we introduce the discrete quantum
theory later. Even if the field of strength is perfectly direct to
the $z$-axis, the variant of velocity makes spots broader and more
washed out. Together with the precision limit of the detector, it
may sometimes hard to decide a particle corresponding to which state.
For higher spins, this bounded resource even limits the ability of
entangled systems to exhibit the violation of Bell's inequalities~\cite{CostaHarriganRudolphEtAl2009}.
Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$.
